An efficient contact value approach to approximating the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-07-14 papers/pair-correlation/paper.tex
fix another CVA-S usage and cut some old todo items Tested on darcy. Took 0:37.79.

\fixme{
  TO DO:
  \begin{itemize}
  \item \davidsays{Rewrite CVA-S section to reflect new fit.  Still working.}
  \item \pahosays{Make certain when proof-reading that other prior
    formulations cannot work in ``separable'' way.}
  \item \davidsays{Be sure that we explain the fitted data and fitting
    process well.  Still working.}
  \item \jeffsays{I will repeatedly read what you guys write!}
  \item \jeffsays{still concerned about the use of CVA.  It seems
    sometimes it's used as an approach and sometimes as the resulting
    pair-dist function.}
  \end{itemize}
}

@@

We begin by examining the lowest-order correction in TPT, given by
Eq.~\ref{eq:mean-field}.  The two terms that are averaged in
Eq.~\ref{eq:g2-our-mean} give equal contributions to the integral:
\begin{align}
  F_1^{\textit{CVA}} &= \tfrac12 \!\! \iint \!\!
  g(r_{12},g_\sigma(\rr_2))n(\rr_1)n(\rr_2)\Phi(|\rr_1-\rr_2|)
  d\rr_1d\rr_2
\end{align}
When we introduce the separable form for $g(r_{12},g_\sigma)$ we can
further simplify this integral as
\begin{multline}
  F_1^{\textit{CVA-S}} =
  \sum_i \tfrac12 \!\! \iint \!\! \bigg( n(\rr_1)  \bigg) \\
                             \bigg( a_i(r_{12})\Phi(r_{12}) \bigg) \\
                             \bigg( b_i(g_\sigma(\rr_2))n(\rr_2) \bigg)
  d\rr_1d\rr_2
\end{multline}
where the functional is written as a summation of integrals, each of
which is an integral of simple convolution in three dimensions.  Thus,
each of these integrals may be computed in $\mathcal{O}(N\log N)$
time, which is the same scaling behavior that is common to the most
common and accurate classical density functional theories, most
notably Fundamental Measure Theory (FMT)~\cite{rosenfeld1989free,
  roth2002whitebear}.

>>>>

\fixme{
  TO DO:
  \begin{itemize}
  \item \jeffsays{still concerned about the use of CVA.  It seems
    sometimes it's used as an approach and sometimes as the resulting
    pair-dist function.}
  \end{itemize}
}

@@

We begin by examining the lowest-order correction in TPT, given by
Eq.~\ref{eq:mean-field}.  The two terms that are averaged in
Eq.~\ref{eq:g2-our-mean} give equal contributions to the integral:
\begin{align}
  F_1^{\textit{CVA}} &= \tfrac12 \!\! \iint \!\!
  g(r_{12},g_\sigma(\rr_2))n(\rr_1)n(\rr_2)\Phi(|\rr_1-\rr_2|)
  d\rr_1d\rr_2
\end{align}
When we introduce the separable form for $g(r_{12},g_\sigma)$ we can
further simplify this integral as
\begin{multline}
  F_1^{\textit{CVA}} =
  \sum_i \tfrac12 \!\! \iint \!\! \bigg( n(\rr_1)  \bigg) \\
                             \bigg( a_i(r_{12})\Phi(r_{12}) \bigg) \\
                             \bigg( b_i(g_\sigma(\rr_2))n(\rr_2) \bigg)
  d\rr_1d\rr_2
\end{multline}
where the functional is written as a summation of integrals, each of
which is an integral of simple convolution in three dimensions.  Thus,
each of these integrals may be computed in $\mathcal{O}(N\log N)$
time, which is the same scaling behavior that is common to the most
common and accurate classical density functional theories, most
notably Fundamental Measure Theory (FMT)~\cite{rosenfeld1989free,
  roth2002whitebear}.
